---
title: "Calculating stock weights"
author: "Kobus Viljoen"
date: "29 September 2016"
output: html_document
---

```{r}
knitr::opts_chunk$set(
  eval = FALSE)
```

##Necessary packages
```{r}
library(broom)
library(modelr)
library(ggplot2)
library(stringr)
library(dplyr)
library(tidyr)
library(purrr)
library(lubridate)
library(tibble)
library(plyr)
#library(FRAPO)
```

In this file I want to calculate the weights assigned to each stock that is selected by the corresponding fundamental factor.
I'm going to use the risk parity approach.
At the end of the stock selection process, I'm left with a tibble with the corresponding quarterly rebalancing dates in a vector and then a list of tibbles with the selected stocks corresponding to the dates.

## Merging the selected stocks with their daily log returns
```{r}
# close_price row number five consist out of the daily closing prices
# log returns are calculated using this function
log_returns <- function(df){
close <- df$"PX_LAST"
date <- dplyr::filter(df,date>date[1]) %>% select(date)
ret <- tibble(date = date$date, log_ret = diff(log(close)))
}

# nesting the daily prices for each stock.
logreturns <- close_prices$data[[5]] %>%
  bind_rows(.id = "Ticker") %>%
  group_by(Ticker) %>%
  nest() %>%
  mutate(logret = map(data,log_returns))  # Mapping the log returns function over each stock's daily close prices


## This function takes the stocks list and dates from a specific model into account in collecting the daily return data for each selected stock for the past year.
# The reason for doing this, is to calculate the risk parity weights, calculating variance/covariance matrix.
Returns <- function(df1,df2){
  Tickers <- df1 %>% select(Ticker)
  logreturns %>%
    unnest(logret) %>%
    group_by(Ticker) %>%
    filter(Ticker %in% Tickers$Ticker) %>%
    filter(date <= df2,date >= df2 - years(2)) %>%
    nest() %>%
    left_join(df1,by = "Ticker")
}
## Example for the Momentum model
# This will be done for each model
Closing <- cross_sec_Fund_data_MOM %>% 
  mutate(returns = map2(stocks,date,Returns))

# Remove the stocks with less than 500 days of data points
# add a column to each returns tibble, which will show the number of rows for a specific share
complete_data <- function(df){
  extension <- df %>% mutate(size = map_dbl(df$data,NROW))
  filter(extension,size >= max(size)-5) %>%
    select(Ticker,data,Market.Cap)
}

Closing <- Closing %>% mutate(returns = map(returns,complete_data))

## Creating a matrix with all the returns for the selected stocks.
Return_Matrix <- function(df){
  joined_data <- df$data %>%
  join_all(by = "date") # Comes from the plyr package
  colnames(joined_data) <- c("date",df$Ticker)
  joined_data
}

Closing <- Closing %>% 
  mutate(ret_matrix = map(returns,Return_Matrix))

## Return matrix for the use of the equal risk contribution methodology.
ERC_WEIGHTS <- function(df){
  cov_matrix <- df[,2:length(colnames(df))] %>%
    cov(use = "complete.obs")
  ERC_weights <- FRAPO::PERC(Sigma = cov_matrix,percentage = FALSE)
  ERC_weights <- as.data.frame(FRAPO::Weights(object = ERC_weights))
  ERC_weights <- tibble(Ticker = c(rownames(ERC_weights)),ERC_Weight = ERC_weights$`FRAPO::Weights(object = ERC_weights)`)
}
Portf_Weights <- Closing %>% 
  mutate(ERCWeights = map(ret_matrix,ERC_WEIGHTS)) %>%
  select(date,ERCWeights)
```

## Market Cap weights for the volatility model
```{r}
MC_weights <- Closing %>% mutate(MC_Weight = map(returns,function(df){
  df %>%
    mutate(MC_Weight = Market.Cap/sum(Market.Cap)) %>%
    select(c(Ticker,MC_Weight))
}))

MC_weights <- MC_weights %>% select(date,MC_Weight)
```


## Risk parity weights
```{r}
# The Portfolio Analytics package is used in order to do the optimisation to estimate the risk parity weights. The risk proxy used is the expected shortfall
# Further investigation will be put into the risk proxy
#install.packages("DEoptim")
#install.packages("ROI")
#install.packages("timeSeries")
#install_github("R-Finance/PortfolioAnalytics")
#install_github("cran/ROI.plugin.glpk")
#install_github("cran/ROI.plugin.quadprog")
library(devtools)
library(DEoptim)
library(ROI)
library(PortfolioAnalytics)
require(ROI.plugin.glpk)
require(ROI.plugin.quadprog)

# This function runs the optimization in order to estimate the risp parity weights, given an xts object.
RP_Weights <- function(df){
returns <- df
rownames(returns) <- returns[[1]]
returns <- as.xts(returns[,2:length(colnames(returns))])
stock_names <- colnames(returns)
pspec <- portfolio.spec(assets = stock_names)
pspec <- add.constraint(portfolio = pspec,
                        type = "weight_sum",
                        min_sum = 1,
                        max_sum =1)
pspec <- add.constraint(portfolio = pspec,
                        type = "box",
                        min = 0.001,
                        max = 0.15)
pspec <- add.objective(portfolio =  pspec ,
                       type= "risk_budget",
                       name = "StdDev",
                       min_concentration = TRUE)
opt <- optimize.portfolio(returns,
                          pspec,
                          optimize_method = "ROI")
RP_weights <- opt$weights
}
# Mapping the optimization function over all the periods
Closing <- Closing %>% mutate(RP_weights = map(ret_matrix,RP_Weights))

# The weights need to be merged with the returns list of tibbles.
# This is done for the risk parity weights
stock_weights <- function(df1,df2){
  df2 %>% 
    left_join(df1 %>% 
                tibble(Ticker = c(Ticker = df2$Ticker),RP_Weight = .),by = "Ticker")
}

## adding the RP, MC and ERC weights 
Closing <- Closing %>% 
  mutate(returns = map2(RP_weights,returns,stock_weights)) %>%
  mutate(returns = map2(returns,MC_weights$MC_Weight,left_join)) %>%
  mutate(returns = map2(returns,Portf_Weights$ERCWeights,left_join))
```

## Calculating the benchmark's performance
```{r}
dates <- Closing$date
JALSH_returns <- JALSH %>% 
  filter(date %in% dates) %>% 
  mutate(JSE_log_ret = c(0,diff(log(PX_LAST)))) %>%
  mutate(JSE_cum_ret = cumprod(1+JSE_log_ret))
SWIX_returns <- SWIX %>%
  filter(date %in% dates) %>%
  mutate(SWIX_log_ret = c(0,diff(log(PX_LAST)))) %>%
  mutate(SWIX_cum_ret = cumprod(1+SWIX_log_ret)) %>%
  select(-PX_LAST)
# There is actually one quarterly date missing in the SWIX data. Wont make difference to cumulative returns at the end.
```


## The total return for each period
```{r}
# The log returns for each asset on the JALSH for each 3 month period
Quarter_logreturns <- close_prices$data[[2]] %>%
  bind_rows(.id = "Ticker") %>%
  group_by(Ticker) %>%
  nest()

log_returns2 <- function(df){
close <- df$"PX_LAST"
date <- dplyr::filter(df,date >= date[1]) %>% select(date)
ret <- tibble(date = date$date, log_ret = c(0,diff(log(close))))
}

Quarter_logreturns <- Quarter_logreturns %>% mutate(logret = map(data,log_returns2))

# leading the dates one period forward in order to get the return achieved over a 3 month period when mapping the Tot_return function
dates <- Closing$date %>% lead()

# This function mutates the corresponding return for an asset over the next 3 months with all the assets selected in the model.
Tot_return <- function(df1,df2){
  Tickers <- df1$Ticker
  b <- Quarter_logreturns %>%
    unnest(logret) %>%
    filter(date == df2,Ticker %in% Tickers) %>%
    right_join(df1,by="Ticker") %>%
    mutate(RP_tot_ret = RP_Weight*log_ret, 
           MC_tot_ret = MC_Weight*log_ret,
           ERC_tot_ret = ERC_Weight*log_ret)
}

# Mapping the function and adding a new list : tot_ret to the closing tibble
# The output, a tibble with all the slected stocks with their corresponding weights and 3 month log returns and total returns (weight*return)
Closing <- Closing %>% 
  mutate(tot_ret = map2(returns,dates,Tot_return))

# get the total return for a 3 month period.
#Mapping a sum_returns function over the total return list in the closing tibble
RP_Ret <- Closing %>% 
  mutate(RP_Ret = map_dbl(tot_ret,function(df) sum(df$RP_tot_ret)),
         MC_Ret = map_dbl(tot_ret,function(df) sum(df$MC_tot_ret)),
         ERC_Ret = map_dbl(tot_ret,function(df) sum(df$ERC_tot_ret))) %>% 
  select(date,RP_Ret,MC_Ret,ERC_Ret)

# adding the cumulative return tibble to the RP_Ret_MOM model
RP_Ret_MOM <- RP_Ret %>% 
  mutate(RP_cum_ret = cumprod(RP_Ret+1) ,
         MC_cum_ret = cumprod(MC_Ret+1),
         ERC_cum_ret = cumprod(ERC_Ret+1)) %>%
  dplyr::rename(Rebalancing_Date = date) %>%
  mutate(date = lead(Rebalancing_Date))

# This tibble gives a summary of the performance up to a specific date.

# Adding the benchmark's performance.
# In this case only the JSE All Share index is used, since it had data from before 2001.
# If another benchmark need to be added, the starting date needs to be changed since I compare cumulative returns
RP_Ret_MOM <- RP_Ret_MOM %>% 
  left_join(JALSH_returns,by = "date") %>% 
  left_join(SWIX_returns,by = "date") %>%
  select(-PX_LAST) %>% 
  dplyr::rename(End_Date = date)
  # The last row still needs to be omitted, since data up to current date are not incorporated 
```

## Combining the macro expsoure of the selected stocks with the tibble containing stock weights
Make sure that the macroeconomic file was executed before the following chunks
```{r}
# A loop is run over all the rebalancing dates in the outer_combine function
# In the inner map function, the macro exposures are combined with their corresponding shares for the specific date.
outer_combine <- function(df,df1){
  exposure <- exposure_per_reb_date_gruber %>% 
    filter(dates == df) %>%
    select(exposure)
  df1 %>%
    mutate(macro_exp = map(Ticker,function(df1){
    ticker <- df1
    model <- exposure$exposure[[1]] %>% filter(Ticker == ticker[[1]])
    macroexp <- tibble(Alpha = model$model[[1]]$coefficients[["(Intercept)"]],
                       ZAR = model$model[[1]]$coefficients[["ZAR_Change"]],
                       OIL = model$model[[1]]$coefficients[["OIL"]],
                       GOLD = model$model[[1]]$coefficients[["GOLD"]],
                       SWAP = model$model[[1]]$coefficients[["SWAP"]])
  }))
}
Macro <- Closing %>% 
  mutate(macro_exp = map2(date,returns,outer_combine)) %>%
  select(date,macro_exp)

#The output can be compared to the specific model's output, to check if all the stocks are included and all their macro exposures are linked up
Macro <- Macro %>% 
  mutate(macro_exp = map(macro_exp,function(df) df %>% unnest(macro_exp)))

```


## Calculating the total macro exposure of the portfolio for a specific month
```{r}
Tot_macro <- function(df){
  exp <- tibble(Alpha = df$RP_Weight*df$Alpha,
                ZAR = df$RP_Weight*df$ZAR,
                OIL = df$RP_Weight*df$OIL,
                GOLD = df$RP_Weight*df$GOLD,
                SWAP = df$RP_Weight*df$SWAP)
  tot_exposure <- tibble(Alpha = sum(exp$Alpha),
                         ZAR = sum(exp$ZAR),
                         OIL = sum(exp$OIL),
                         GOLD = sum(exp$GOLD),
                         SWAP = sum(exp$SWAP))
}
Total_exposure <- Macro %>% mutate(tot_exp = map(macro_exp,Tot_macro))
Total_exposure <- Total_exposure %>% unnest(tot_exp)
```


