---
title: "importing data from bloomberg"
author: "Kobus Viljoen"
date: "28 September 2016"
output: html_document
---

##Installing packages to extract data from bloomberg and clean my data

```{r installing ,eval=FALSE}
install.packages(c("dplyr","tidyr","purrr","lubridate","Rblpapi"))
library(dplyr)
library(tidyr)
library(purrr)
library(lubridate)
library(Rblpapi)
```


##Setup a connection with bloomberg
```{r ,eval=FALSE}
con <- blpConnect()
```

An equity screen is done to extract all of the stocks listed on the JSE All Share Index
The screen's name is AllData, it also looks at the relevant fundamental factors of the stocks.
This was also done as a test, to see if I could do an equity screen from inside R.
```{r , eval=FALSE}
# This is done, just to get a base of the tickers in order to extract daily,weekly,monthly ect. data and to get the corresponding rebalancing dates
eqs15 <- beqs(screenName = "AllData",date = ymd("20150101"))
TickerNames15 <- eqs15$Ticker
```

##Closing prices extraction from bloomberg
Different periodic sample lengths are created. This is used in a tibble and a function is mapped over all the different periodic samples, extracting periodic closing prices from bloomberg
```{r,eval=FALSE}
monthly <- c("periodicitySelection"="MONTHLY",
           "periodicityAdjustment"="CALENDAR")
quarterly <- c("periodicitySelection"="QUARTERLY",
               "periodicityAdjustment"="CALENDAR")
halfyearly <- c("periodicitySelection"="SEMI_ANNUALLY",
                "periodicityAdjustment"="CALENDAR")
yearly <- c("periodicitySelection"="YEARLY",
              "periodicityAdjustment"="CALENDAR")
daily <- c("periodicitySelection"="DAILY",
            "periodicityAdjustment"="CALENDAR")
weekly <- c("periodicitySelection"="WEEKLY",
            "periodicityAdjustment"="CALENDAR")
close_prices <- tibble(selection = list(monthly,quarterly,halfyearly,yearly,daily,weekly),
       data = map(selection,function(selection){
         bdh(securities = as.character(TickerNames15),
             fields = "PX_LAST",
             start.date=ymd("2002-01-01"),
             options=selection)
       }))
```

## Importing data for cross sectional selection
```{r}
dates <- close_prices$data[[2]]$`SOL SJ Equity`$date
cross_sec_Fund_data <- tibble(date = dates)

eqs1 <- function(df){
  beqs(screenName = "AllData",date = ymd(df))
}

cross_sec_Fund_data <- cross_sec_Fund_data %>%
  mutate(Fundamental = map(date,eqs1))

## Need to extract all of the Tickers now, using all of the equity screen results and run the close prices function again, the one in the previous chunk.
unlisted_data <- cross_sec_Fund_data %>% unnest(Fundamental)
TickerNames <- unlisted_data$Ticker %>% unique()

close_prices <- tibble(selection = list(monthly,quarterly,halfyearly,yearly,daily,weekly),
       data = map(selection,function(selection){
         bdh(securities = as.character(TickerNames),
             fields = "PX_LAST",
             start.date=ymd("1999-01-01"),
             options=selection)
       }))
## Should use 3 years data for RP weight calculation

```

##Extracting daily fundamental data for each stock
A tibble is created with a character vector with all the fundamental factors' names. A function is written that will extract daily data for each of these fundamentals in the tibble with the map function in R.
```{r,eval=FALSE}
fields <- tibble(fields = c("CUR_MKT_CAP",
                            "PX_LAST",
                            "PX_TO_BOOK_RATIO",
                            "RETURN_COM_EQY",
                            "EQY_DVD_YLD_12M",
                            "GROSS_PROFIT",
                            "EARN_YLD_HIST",
                            "VOLATILITY_60D",
                            "VOLATILITY_260D",
                            "PX_VOLUME"))

extract_daily <- function(df){
  bdh(securities = as.character(TickerNames),
      fields = df,
      start.date = ymd("20000101"),
      options = daily)
}

Fundamental_Data <- fields %>%
  mutate(Fund_Data = map(fields,extract_daily))
```

## Daily and weekly data of macroeconomic data
```{r}
OIL_daily <- bdh("CL1 Comdty",
           fields = "PX_LAST",
           start.date = ymd("20000101"))
ZAR_daily <- bdh("ZAR Curncy",
           fields = "PX_LAST",
           start.date = ymd("20000101"))
GOLD_daily <- bdh("GC1 Comdty",
           fields = "PX_LAST",
           start.date = ymd("20000101"))
SWAP_daily <- bdh("SASW10 Curncy",
           fields = "PX_LAST",
           start.date = ymd("20000101"))
SA_Bond_daily <- bdh("GSAB10YR Index",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = daily)


OIL_weekly <- bdh("CL1 Comdty",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = weekly)
ZAR_weekly <- bdh("ZAR Curncy",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = weekly)
GOLD_weekly <- bdh("GC1 Comdty",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = weekly)
SWAP_weekly <- bdh("SASW10 Curncy",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = weekly)
GDP_weekly <- bdh("SACGDP Index",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = weekly)
SA_Bond_weekly <- bdh("GSAB10YR Index",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = weekly)
```

## benchmark performances
```{r}
# The JASLH and SWIX are extracted now, further attention will be given to the correct benchmark.
JALSH <- bdh("JALSH Index",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = daily)
SWIX <- bdh("JSHRALTR Index",
           fields = "PX_LAST",
           start.date = ymd("20000101"),
           options = daily)
```








