---
title: "importing data from bloomberg"
author: "Kobus Viljoen"
date: "28 September 2016"
output: html_document
---

##Installing packages to extract data from bloomberg and clean my data

```{r installing ,eval=FALSE}
install.packages(c("dplyr","tidyr","purrr","lubridate","Rblpapi"))
library(dplyr)
library(tidyr)
library(purrr)
library(lubridate)
library(Rblpapi)
```


##Setup a connection with bloomberg
```{r ,eval=FALSE}
con <- blpConnect()
```

An equity screen is done to extract all of the stocks listed on the JSE All Share Index
The screen's name is AllData, it also looks at the relevant fundamental factors of the stocks
```{r , eval=FALSE}
eqs15 <- beqs(screenName = "AllData",date = ymd("20150101"))
TickerNames15 <- eqs15$Ticker
```

##Closing prices extraction from bloomberg
Different periodic sample lengths are created. This is used in a tibble and a function is mapped over all the different periodic samples, extracting periodic closing prices from bloomberg
```{r,eval=FALSE}
monthly <- c("periodicitySelection"="MONTHLY",
           "periodicityAdjustment"="CALENDAR")
quarterly <- c("periodicitySelection"="QUARTERLY",
               "periodicityAdjustment"="CALENDAR")
halfyearly <- c("periodicitySelection"="SEMI_ANNUALLY",
                "periodicityAdjustment"="CALENDAR")
yearly <- c("periodicitySelection"="YEARLY",
              "periodicityAdjustment"="CALENDAR")
daily <- c("periodicitySelection"="DAILY",
            "periodicityAdjustment"="CALENDAR")
close_prices <- tibble(selection = list(monthly,quarterly,halfyearly,yearly,daily),
       data = map(selection,function(selection){
         bdh(securities = as.character(TickerNames15),
             fields = "PX_LAST",
             start.date=ymd("1998-01-01"),
             options=selection)
       }))
```

##Extracting daily fundamental data for each stock
A tibble is created with a character vector with all the fundamental factors' names. A function is written that will extract daily data for each of these fundamentals in the tibble with the map function in R.
```{r,eval=FALSE}
fields <- tibble(fields = c("CUR_MKT_CAP",
                            "PX_LAST",
                            "PX_TO_BOOK_RATIO",
                            "RETURN_COM_EQY",
                            "EQY_DVD_YLD_12M",
                            "AVG_VOL",
                            "VOLATILITY_260D"))

extract_daily <- function(df){
  bdh(securities = as.character(TickerNames15),
      fields = df,
      start.date = ymd("19980101"),
      options = daily)
}

Fundamental_Data <- fields %>%
  mutate(Fund_Data = map(fields,extract_daily))
```

Macroeconomic factors will be extracted at a later stage. These will be used for the macroeconomic exposure model.
