---
title: "Macro-Economic Exposure"
author: "Kobus Viljoen"
date: "14 October 2016"
output: html_document
---

```{r}
knitr::opts_chunk$set(
  eval = FALSE)
```

## Necessary packages
```{r}
library(quantmod)
library(broom)
library(modelr)
library(ggplot2)
library(stringr)
library(dplyr)
library(tidyr)
library(purrr)
library(lubridate)
```

## Calculating weekly log returns for all the shares and macro factors
This will be done for all the shares so that, with the stock selection process, i could just filter the necessary stocks and their exposure for a given rebalncing date.
```{r}
## exclude NA's due to OIL and GOLD being american data, some dates may be missing
options(na.action = na.exclude)
## daily per share date for fitting macro model for each share
per_share <- close_prices$data[[6]] %>% 
  bind_rows(.id="Ticker") %>% 
  group_by(Ticker) %>% 
  nest()

## Calculates Daily log Return and put into Tibble
log_returns <- function(df){
  close <- df$"PX_LAST"
  date <- filter(df,date>date[1]) %>% select(date)
  ret <- tibble(date = date$date, log_ret = diff(log(close)))
}
## Calculate macroeconomic changes
ZAR_change <- log_returns(ZAR_weekly) %>% dplyr::rename(ZAR_Change = log_ret)
Oil_change <- log_returns(OIL_weekly) %>% dplyr::rename(OIL_Change = log_ret)
GOLD_change <- log_returns(GOLD_weekly) %>% dplyr::rename(GOLD_Change = log_ret)
SWAP_change <- log_returns(SWAP_weekly) %>% dplyr::rename(SWAP_Change = log_ret)
############## Need to get data for 10y bond and also CPI

### This function is created twice due to the macro factors added in the second one.
log_returns <- function(df){
  close <- df$"PX_LAST"
  date <- filter(df,date>date[1]) %>% select(date)
  ret <- tibble(date = date$date, log_ret = diff(log(close))) %>%
    merge(ZAR_change) %>%
    merge(Oil_change) %>%
    merge(GOLD_change) %>%
    merge(SWAP_change)
}

## add weekly log returns to the weekly per_share data and also the weekly the change in macro factors
## The macro factors are added for each share, it is easier to do a regression that way.
## i know that the dates match
per_share <- per_share %>% mutate(ret = map(data,log_returns))
```

## Grouping the data according to the rebalancing dates
A tibble with the rebalancing dates are created at first.
Yearly data for each stock, up to a rebalncing date, are put into the next column as a list of tibbles
```{r}
dates <- close_prices$data[[2]] %>% 
  bind_rows(.id="Ticker") %>% 
  group_by(date) %>% 
  nest() %>%
  filter(date >= date[13]) %>%
  select(date)

# Creating a tibble with the rebalancing dates
macro_per_share <- tibble(dates = dates$date)

# Getting the data for each stock for the past year for the corresponding date
collect_data <- function(df){
  per_share %>% 
    unnest(ret) %>%
    filter(date <= df,date >= df - years(1)) %>%
    group_by(Ticker) %>%
    nest()
}

macro_per_share <- macro_per_share %>% 
  mutate(data = map(dates,collect_data))
```

## Calculating the macro exposure of each stock using Gruber
This is based on a time series regression over the past 52 weeks
4 linear regression functions are written, in order to make the macro factors uncorrelated with each other.

```{r}
macro_exposure <- function(df){
  macro_model <- function(df){
    lm(OIL_Change ~ ZAR_Change, data = df)
  }
  
  macro1 <- df %>% mutate(model = map(data,macro_model))
  macro1 <- macro1 %>% mutate(resids = map2(data,model,add_residuals))
  
  macro1 <- macro1 %>% unnest(resids) %>% dplyr::rename(OIL = resid) %>% group_by(Ticker) %>% nest()
  
  
  macro_model <- function(df){
    lm(GOLD_Change ~ ZAR_Change + OIL, data = df)
  }
  macro2 <- macro1 %>% mutate(model = map(data,macro_model))
  macro2 <- macro2 %>% mutate(resids = map2(data,model,add_residuals))
  
  macro2 <- macro2 %>% unnest(resids) %>% dplyr::rename(GOLD = resid) %>% group_by(Ticker) %>% nest()
  
  macro_model <- function(df){
    lm(SWAP_Change ~ ZAR_Change + OIL + GOLD, data = df)
  }
  macro3 <- macro2 %>% mutate(model = map(data,macro_model))
  macro3 <- macro3 %>% mutate(resids = map2(data,model,add_residuals))
  
  macro3 <- macro3 %>% unnest(resids) %>% dplyr::rename(SWAP = resid) %>% group_by(Ticker) %>% nest()
  
  
  macro_model <- function(df){
    lm(log_ret ~ ZAR_Change + OIL + GOLD + SWAP , data = df)
  }
  
  macro_final <- macro3 %>% mutate(model = map(data,macro_model))
  macro_final <- macro_final %>% mutate(resids = map2(data,model,add_residuals))
  
  
}
# This function of linear regression functions are mapped over all the rebalancing dates and over all the stocks, given their yearly data up to that specific date
exposure_per_reb_date_gruber <- macro_per_share %>% mutate(exposure = map(data,macro_exposure))
```

